%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins
\usepackage{hyperref}

\name{Chih-cheng Rex Yuan} % Your name
%\address{123 Broadway \\ City, State 12345} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{\href[pdfnewwindow=true]{https://github.com/RexYuan}{github.com/RexYuan}}
\address{\href[pdfnewwindow=true]{https://www.linkedin.com/in/rexyuan/}{linkedin.com/in/rexyuan}}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf National Taiwan Normal University} \hfill {2014 - 2019} \\
{\em B.S. in Computer Science and Information Engineering}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

{\bf Institute of Information Science, Academia Sinica} \hfill {2023 - Present} \\
{\em Research Assistant} \hfill {\em Hybrid}
\smallskip

\begin{rSubsection}{SiFive}{2022 - 2023}{Hardware Engineer}{Hybrid}
\item System validation of regression automation tools in Bash and Perl.
\item Communication with a range of teams regarding distinct issues.
\end{rSubsection}

\begin{rSubsection}{Formal Land}{2022}{Software Engineer}{Remote}
\item Formal verification of the OCaml codebase of Tezos blockchains protocol in Coq.
\item Collaboration with a geographically-dispersed team across 5 timezones.
\end{rSubsection}

\begin{rSubsection}{Institute of Information Science, Academia Sinica}{2019 - 2022}{Research Assistant}{Hybrid}
\item Formal verification research of hardware safety algorithms.
\item Organization of an academic conference (ATVA19) and assisted multiple international guests.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Institute of Information Science, Academia Sinica}{2017 – 2019}{Adjunct Research Assistant}{Hybrid}
\item Formal methods research using SAT solvers on chart synthesis and privacy de-identification.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Inside.com.tw}{2016}{Software Engineering Intern}{On-site}
\item Back-end WordPress theme development in PHP. Collaborated with an external front-end team.
\item Internal editor UI/UX feature requests fulfillment and manual writing for the editorial team.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Inside.com.tw}{2015}{Editorial Intern}{On-site}
\item Interview and research coverage on Taiwanese technology and start-up scenes.
\item Translation and localization of external drafts and press releases from en to zh.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Volunteering}

\begin{list}{$\cdot$}{\leftmargin=0em}
\itemsep -0.5em
\item I run a Facebook meme page for logic (\href[pdfnewwindow=true]{https://www.facebook.com/FormalMemes}{facebook.com/FormalMemes}). \hfill {2018 - Present}
\item Translator for Mozilla. \hfill {2016 - 2018}
\item VP of a school club with that collaborated with Mozilla and Wikimedia. \hfill {2016 - 2018}
\item Founded a student-run organization that digitize school information. \hfill {2014 - 2019}
\item Member of a local decentralised civic tech community (g0v). \hfill {2015}
\end{list}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
