%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins

\name{Chih-cheng Rex Yuan} % Your name
%\address{123 Broadway \\ City, State 12345} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{hello@rexyuan.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf National Taiwan Normal University} \hfill {2014 - 2019} \\
{\em B.S. in Computer Science and Information Engineering}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Institute of Information Science, Academia Sinica}{2019 - Present}{Research Assistant}{}
\item Developed bit-level hardware verification safety algorithm based on algorithmic boolean learning and
interpolation.
\item implemented AIG input parser, C++ minisat API, memory arena, and custom profiling and logging.
\item Worked on algorithmic learning such as order-theoretical version space learning, automata L* regular language learning,
and monotone-theoretical CDNF boolean function learning.
\item Worked on formal methods such as syntax-guided program synthesis, counterexample-guided abstraction refinement,
and bounded temporal unrolling.
\item Worked on logical theories such as propositional Craig interpolation, boolean theory, and boolean analysis.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Institute of Information Science, Academia Sinica}{2017 – 2019}{Adjunct Research Assistant}{}
\item SAT-solving reduction of poset cover problem for message sequence chart synthesis  implemented in Python with z3.
\item NP-hardness of k-anonymity checking problem and a randomized approach thereof for the 2010 Taiwanese census data
implemented in Python with MySQL.
\item Worked on connection between order theory and langauge theory, proving that between permuted linearizations
and Myhill-Nerode theorem.
\item Worked on de-identification techniques such as $\ell$-diversity, $t$-closeness, and $\delta$-presence.
\item Worked on differential privacy framework in Pufferfish.
\item Worked on probabilistic programming in WebPPL.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Inside.com.tw}{2016}{Software Engineering Intern}{}
\item Backend Wordpress theme development; collaboration  and communication with frontend team.
\item In-house editor user-interface feature requests for editorial team.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Inside.com.tw}{2015}{Editorial Intern}{}
\item Coverage, interviewing, and reporting on technology and startup related scenes.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards \& Certificates}

{\bf Academic Excellence Award} \hfill {2016} \\
{\em Ranked top 5\% in a class} \\
{\bf TOEFL iBT} \hfill {2016} \\
{\em Score: 108 (Reading: 29 / Listening: 30 / Speaking: 22 / Writing: 27)} \\
{\bf TOEIC} \hfill {2013} \\
{\em Score: 960}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
