%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.5in,top=0.5in,right=0.5in,bottom=0.5in]{geometry} % Document margins

\name{Chih-cheng Rex Yuan} % Your name
%\address{123 Broadway \\ City, State 12345} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{hello@rexyuan.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf National Taiwan Normal University} \hfill {2014 - 2019} \\
{\em B.S. in Computer Science and Information Engineering}

{\bf FLOLAC Summer School at National Taiwan University} \hfill {2017, 2018, 2019} \\
{\bf CONFESTA Summer School at University of Chinese Academy of Sciences} \hfill {2018}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{SiFive}{2022 - 2023}{Hardware Engineer}{}
\item System validation of regression automation tools in Bash and Perl.
\end{rSubsection}

\begin{rSubsection}{Formal Land}{2022}{Software Engineer}{}
\item Formal verification of the OCaml codebase of Tezos blockchains protocol in Coq.
\end{rSubsection}

\begin{rSubsection}{Institute of Information Science, Academia Sinica}{2019 - 2022}{Research Assistant}{}
\item Developed and optimized bit-level hardware verification safety algorithm
 based on algorithmic boolean learning and logical interpolation in C++ with minisat.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Institute of Information Science, Academia Sinica}{2017 – 2019}{Adjunct Research Assistant}{}
\item SAT-solving reduction of poset cover problem for message sequence chart synthesis  implemented in Python with z3.
\item NP-hardness of k-anonymity checking problem and a randomized approach thereof for the 2010 Taiwanese census data
implemented in Python with MySQL.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Inside.com.tw}{2016}{Software Engineering Intern}{}
\item Back-end WordPress theme development in PHP. Collaborated with an external front-end team.
\item News feed delivery Facebook chatbot made with off-the-shelf software.
\item Internal editor UI/UX feature requests fulfillment and manual writing for the editorial team.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Inside.com.tw}{2015}{Editorial Intern}{}
\item Interview and research coverage on Taiwanese technology and start-up scenes.
\item Translation and localization of external drafts and press releases from en to zh.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards \& Certificates}

{\bf Academic Excellence Award} \hfill {2016} \\
{\em Ranked top 5\% in a class} \\
{\bf TOEFL iBT} \hfill {2016} \\
{\em Score: 108 (Reading: 29 / Listening: 30 / Speaking: 22 / Writing: 27)} \\
{\bf TOEIC} \hfill {2013} \\
{\em Score: 960 (Reading: 480 / Listening: 480)}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
